Appendix B: Examples of Deep RL in Ecological Decision Problems

### 2021-06-04 appendices/appendix-B-examples.Rmd
instability...

Good choices for hyper-parameters can be found through a process known as "hyper-parameter tuning", which uses standard function optimization approaches to vary the choice of hyper-parameters to determine which hyper-parameters maximize the agent's performance. 
For simplicity, we show only training with specified hyper-parameters here, found by various tuning experimentation (see <https://github.com/boettiger-lab/conservation-agents>) or the standard reference examples presented in `stable-baselines3-zoo` [@zoo].

```{r}
env = sb3$common$env_util$make_vec_env("fishing-v1", n_envs=4L, seed=seed)

# Create a fishing environment
# Create an agent
ppo_tuned = sb3$PPO("MlpPolicy",
                    "env" = env, 
                    "seed" = seed,
                    "batch_size" = 64L,
                    "n_steps" = 32L,
                    "gamma" = 0.9999,
                    "learning_rate" = 0.00038,
                    "ent_coef" = 0.0,
                    "clip_range" = 0.3,
                    "n_epochs" = 10L,
                    "gae_lambda" = 0.92,
                    "max_grad_norm" = 0.7,
                    "vf_coef" = 0.486355,
                    "policy_kwargs" = list(
                      "net_arch" = c(64L, 64L),
                      "activation_fn" = torch$nn$ReLU
                     )
                   )

@@

We train this new PPO-based agent as before:

>>>>

Good choices for hyper-parameters can be found through a process known as "hyper-parameter tuning", which uses standard function optimization approaches to vary the choice of hyper-parameters to determine which hyper-parameters maximize the agent's performance.
In practice, tuning may attempt to set only a subset of parameters through an optimal search algorithm, while others are chosen manually.
Because each iteration in tuning must retrain the algorithm over thousands or millions of episodes, tuning can easily become very computationally intensive.
For simplicity, here we illustrate how to train PPO using custom hyperparameters.
The PPO algorithm supports training on a vectorized environment, in which the algorithm learns by interacting with `n` independent copies of the environment simultaneously.
The choice of `n` can itself be considered another hyperparameter.
Additional choices for many of the hyperparameters used by the PPO model are specified as additional optional arguments.
In this case, the parameter choices shown were already derived through tuning (see <https://github.com/boettiger-lab/conservation-agents>, or the standard reference examples presented in `stable-baselines3-zoo` [@zoo]).
More generally, these choices could represent any alternative trial of possible hyperparameters.

```{r}
vec_env = sb3$common$env_util$make_vec_env("fishing-v1", n_envs=4L, seed=seed)

# Create a fishing environment
# Create an agent
ppo_tuned = sb3$PPO("MlpPolicy",
                    "env" = vec_env, 
                    "seed" = seed,
                    "batch_size" = 64L,
                    "n_steps" = 32L,
                    "gamma" = 0.9999,
                    "learning_rate" = 0.00037996229760279524,
                    "ent_coef" = 2.392750198613048e-08,
                    "clip_range" = 0.3,
                    "n_epochs" = 10L,
                    "gae_lambda" = 0.92,
                    "max_grad_norm" = 0.7,
                    "vf_coef" = 0.4863551514846155,
                    "policy_kwargs" = list(
                      "net_arch" = c(64L, 64L),
                      "activation_fn" = torch$nn$ReLU
                     )
                   )

@@

We train this new PPO-based agent for 300,000 steps, as before:
